MLH1 data report 

### 2017-10-27 rmd_report.rmd
refining make file

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
library(pwr)
library(plyr)
library(lattice)
library(dplyr)
#setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")
```

>>>>

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")
```
